Open Source, Collaborative Curriculum

### 2017-04-17 siip.tex
siip comments uncommented

\usepackage[acronym,toc]{glossaries}
\include{acros}
\makeglossaries
\usepackage{fancyhdr}
\usepackage{pagecounting}
\usepackage[dvips]{color}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[hidelinks]{hyperref}

@@

          \begin{document}

          \pagestyle{fancy}
          %\pagenumbering{gobble}
          %\fancyhead[location]{text}
          % Leave Left and Right Header empty.
          %\lhead{}
          %\rhead{}
          \lhead{\textcolor{gray}{PI: \authorname (NPRE)\\\authoremail}}
          \rhead{\textcolor{gray}{SIIP Pre-Proposal\\}}
          %\rhead{\textcolor{gray}{\thepage/\totalpages{}}}
          \renewcommand{\headrulewidth}{0pt}
          \renewcommand{\footrulewidth}{0pt}
          \fancyfoot[C]{\footnotesize \textcolor{gray}{\authorsite}}

@@

\iffalse
          New features are described in 
          tickets and discussed before implementation. Small, atomic changes 
          are reviewed before merging. Communities of practice are nurtured.

@@

          \begin{figure}
                  \centering
                  \begin{subfigure}{.4\textwidth}
                            \centering
                              \includegraphics[width=.8\linewidth]{git-flow}
        \caption{This figure, from \cite{scopatz_effective_2016}, captures a process, often called Git Flow, through which a new feature or bug fix enters a piece of open source software \cite{scopatz_effective_2016}.}
                                  \label{fig:sub1}
                  \end{subfigure}\hfill%
                  \begin{subfigure}{.4\textwidth}
                            \centering
                              \includegraphics[width=.8\linewidth]{siip-flow}
  \caption{This adaptation imagines the process in the context of learning module development, using the same git version control system and GitHub repository hosting framework.}
                                  \label{fig:sub2}
                  \end{subfigure}
                  \label{fig:test}
          \end{figure}

\fi

>>>>

\usepackage[acronym,toc]{glossaries}
\include{acros}
\makeglossaries
\usepackage{fancyhdr}
\usepackage{pagecounting}
\usepackage[dvips]{color}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{placeins}
\usepackage[hidelinks]{hyperref}

@@

          \begin{document}
          \title{Open Source, Collaborative Curriculum}
          \author{PI: Kathryn Huff\\Co-PI: Neal Davis}
          \maketitle

          \pagestyle{fancy}
          %\pagenumbering{gobble}
          %\fancyhead[location]{text}
          % Leave Left and Right Header empty.
          %\lhead{}
          %\rhead{}
          \lhead{\textcolor{gray}{PI: \authorname (NPRE)\\\authoremail}}
          \rhead{\textcolor{gray}{Collaborative Open Source Curriculum Development\\}}
          %\rhead{\textcolor{gray}{\thepage/\totalpages{}}}
          \renewcommand{\headrulewidth}{0pt}
          \renewcommand{\footrulewidth}{0pt}
          \fancyfoot[C]{\footnotesize \textcolor{gray}{\authorsite}}

@@

          Development of this proof-of-concept curriculum will be undertaken 
          similarly to an open source software project.

          Some features of open source development that will be emulated 
          include those that cultivate collaboration. In open source, 
          for example, new code features are described in tickets and discussed 
          before implementation. Small, atomic changes are reviewed before 
          merging. Through these discussions and incremental reviews, communities of practice are nurtured.

@@

          \begin{figure}
                  \centering
                  \begin{subfigure}{.4\textwidth}
                            \centering
                              \includegraphics[width=.8\linewidth]{git-flow}
        \caption{This figure, from \cite{scopatz_effective_2016}, captures a process, often called Git Flow, through which a new feature or bug fix enters a piece of open source software \cite{scopatz_effective_2016}.}
                                  \label{fig:sub1}
                  \end{subfigure}\hfill%
                  \begin{subfigure}{.4\textwidth}
                            \centering
                              \includegraphics[width=.8\linewidth]{siip-flow}
  \caption{This adaptation imagines the process in the context of learning module development, using the same git version control system and GitHub repository hosting framework.}
                                  \label{fig:sub2}
                  \end{subfigure}
                  \label{fig:test}
          \end{figure}
          \FloatBarrier
